\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas
updates

%%%%%%%%%%%%%
\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}    
\medskip

>>>>

%%%%%%%%%%%%%
\subsection{Capturing Fingering Formation with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most geofluid numerical simulations, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably assimilate the information
